The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
fix lab pos winlen, winpos

Similarly, shifting window position of the summer season resulted in an increase in number of connections between individuals. Layer relevance

@@

Shifting window position results showed increasing layer similarity

>>>>

<!-- Similarly, shifting window position of the summer season resulted in an increase in number of connections between individuals. Layer relevance  -->

@@

<!-- Shifting window position results showed increasing layer similarity  -->

**Missing: discussion of window position..**
